``A rose by any other name would smell as sweet'': \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-31 paper/paper.tex
incorporated the rest of Bill's feedback

\subsection{Modern Translations}
Access to parallel text in the target style allows us to train statistical models to generate paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires availability of reference translations.  For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us two reference translations for 8 out of the 17 plays.

After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence aligner \cite{Moore02}, which produced about 21,079 alignments out of 31,718 sentences in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the Enotes data.  The modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the Enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
original text; the Sparknotes paraphrases result in a BLEU score of 24.67, whereas the Enotes paraphrases produce a much higher BLEU of 52.30 indicating their strong similarity to the original plays.
These corpus statistics are summarized in table \ref{corpus_stats}.

@@

\subsection{Baselines}
Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}, however this approach does require the existence of
parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
quantify the benefit of access to parallel text in the source and target styles.

@@

To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
example dictionary entries are presented in table \ref{dictionary_example}. 
As described in \cite{Koehn00}, we estimate phrase translation probabilities
based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
We obtained the conditional probabilities for each translation according to the n-gram back off model built on Shakespeare's 
36 plays by SRILM toolkit \cite{Stolcke02} \ref{word_frequency}, 
normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$. 
This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
with a language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet}), which are then fed into the Moses decoder
\cite{Koehn07}.

@@

\subsubsection{Out of Domain Monolingual Parallel Data}
\label{video_baseline}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of domain parallel text, with an in-domain
language model consisting of Shakespeare's 36 plays (holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the system's output towards Shakespeare's style of writing.
We found that performing Minimum Error Rate Training using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
video corpus baseline to generate reasonable paraphrases.

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of systems targeting Shakespearean English using the previously proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics which
have been demonstrated to correlate with human judgments on semantic adequacy and lexical dissimilarity with the input.
A description of each of the systems compared in this experiment is presented in table \ref{systems}.  Notice that the Enotes paraphrases are quite similar to the original text,
obtaining a BLEU score of 52.3 when compared directly to the original lines from Shakespeare's plays.  Because our goal is to produce paraphrases which make more dramatic stylistic changes to the input,
in the remainder of this paper, we focus on the Sparknotes data for evaluation.

\subsubsection{Discussion}
Two main trends emerge from Figure \ref{bleupinc}.  First, notice that all of the systems which are trained using parallel text achieve higher BLEU scores than the baseline
of not making any changes to the modern translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
input, its BLEU is lower than the \emph{no changes} baseline.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training \cite{MERT}
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, however also not seeing any BLEU improvements on the test data.  Finally
we note that using the larger language model seems to yield a slight improvement in BLEU score.

@@

\begin{table}
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in section \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in section \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

\section{Human Evaluation}
\label{human_evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is initially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases targeting a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, however no
previous work has evaluated automatically generated paraphrases which target a specific style of writing.

While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it may also depend on style, since utterances
are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU doesn't tell us, however
is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.

For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and its Shakespearean
translation with semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
The aggregate results of the human evaluation are displayed in figure \ref{human_judgements}.  Agreement between annotators
measured using Pearson's $\rho$ is displayed in table \ref{annotator_agreement}.

Based on the human evaluation, it appears that the baseline combining paraphrases collected from mechanical Turk \cite{chen11} with
a Shakespearean language model has the highest semantic adequacy, however it is also fairly conservative making few changes to the input.

The dictionary baseline, and paraphrase system trained on parallel modern translations are roughly comparable when it comes to 
the number of changes made to the input, however the system trained on modern translations achieves higher semantic adequacy, while also being rated higher on style and overall.

These results are roughly in line with the automatic evaluation metrics presented in figure \ref{bleupinc}, however we also see several important
trends which are not apparent from the automatic evaluation.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating paraphrases targeting a  writing style, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
to separate effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
between a system which generates perfect paraphrases which don't match the target style of writing and a system which
generates sentences in the correct style, but which convey different meaning.

@@

We present a preliminary evaluation of these metrics by measuring their correlation with human judgments, however
we emphasize that we are only evaluating these metrics with respect to one specific style of writing.  We
are cautiously optimistic that our results will generalize across writing styles, however, as they are based entirely
on ngram statistics.

@@

\subsection{Evaluation}
We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
evaluation metrics and human judgments described in section \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

@@

As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
due to the conflation of stylistic differences and semantic adequacy discussed discussed in section \ref{human_evaluation}, however it also appears 
that the correlation between BLEU and human style judgments is too low to be of practical use for evaluating style.

@@

\section{Translating Shakespeare's Plays to Modern English}
Finally we preform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  Success at this task could have immediate
benefits to students, as well as translators of Shakespeare's plays into modern English.

For the purposes of this evaluation, 
we make use of the same paraphrase systems previously described, but swap the source and target languages.
Additionally, each system makes use of a language model constructed from the 16 modern translations, and again Romeo and Juliet are held out for testing.  
510 lines from Romeo and Juliet were automatically translated into modern English using each system, and the aligned modern 
translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
data are presented in figure \ref{shakespeare_to_modern_automatic}.

@@

\begin{figure}
  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern english comparing a system based on parallel text (16plays\_16LM), 
  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overal
  PINC score, as few phrases in the input match phrases found in its phrase table, resulting in a small number of changes to the input.}
  \label{shakespeare_to_modern_automatic}
\end{figure}

@@

Perhaps most relevant, however, is recent work autoatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, however does not investigate the task of paraphrase.  Their generation system
is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
While our work does not address the issue of meter, it should be possible to combine our translation
models with their weighted finite state transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.

@@

\section{Conclusions}
We have presented initial investigation into the task of automatic paraphrasing while targeting a specific style of writing.  We proposed Shakespeare's plays and their
modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
perform better according to each criteria.

To address this problem, we have introduced two new metrics for evaluating writing style.
We measured correlation between automatic metrics and human judgments, and showed
that our new metrics have better correlation with human judgments than existing metrics in the context of our task.
While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
evaluating paraphrase systems targeting other writing styles.

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
of Shakespeare and also to human translators.

>>>>

\subsection{Modern Translations}
\label{modern_translations}
Access to parallel text in the target style allows us to train statistical models that generate paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires availability of reference translations.  For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and 
additional translations of 8 of these plays from from \url{http://enotes.com}.

After tokenizing and lowercasing, the plays were sentence aligned \cite{Moore02}, producing 21,079 alignments from the 31,718 sentence pairs in the Sparknotes data, and 10,365 sentence pairs from the 13,640 original 
pairs in the Enotes data.  The modern translations from the two sources are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the Enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the modern translations against Shakespeare's 
original text; the Sparknotes paraphrases yield a BLEU score of 24.67, whereas the Enotes paraphrases produce a much higher BLEU of 52.30 reflecting their strong similarity to the original texts.
These results are summarized in table \ref{corpus_stats}.

@@

\subsection{Baselines}
Phrase-based translation has been demonstrated as an effective approach to paraphrasing \cite{quirk04,chen11}.  However, this approach does require the existence of
parallel corpora, resources which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches in order to help
quantify the benefit of access to parallel text in the source and target styles.

@@

To build a phrase table, we scraped a set of 68,709 phrase/word pairs from \url{http://www.shakespeareswords.com/}; 
example dictionary entries are presented in table \ref{dictionary_example}. 
As described in \cite{Koehn00}, we estimate phrase translation probabilities
based on the frequencies of the translation words/phrases in the target language (Shakespearean English).
For instance, if we look at the modern English word \emph{maybe}, our dictionary lists 4 possible Shakespearean translations. 
We obtained the conditional probabilities for each translation according to the n-gram back-off model built from 36 of Shakespeare's 
plays ({\em Romeo and Juliet} was held out for testing) using the SRILM toolkit \cite{Stolcke02}, 
normalizing the probabilities for each source phrase, for example $p(\text{PERCHANGE}|\text{maybe}) = \frac{0.0000790755}{0.00026264791} = 0.30107035689$.
An example is presented in Table \ref{word_frequency}.
This method allows us to estimate reasonable translation probabilities for use in a phrase table, which is used in combination 
with a language model built from the 36 plays, which are then fed into the Moses decoder \cite{Koehn07}.

@@

\subsubsection{Out of Domain Monolingual Parallel Data}
\label{video_baseline}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this modern, out of domain parallel text, with an in-domain
language model consisting of Shakespeare's 36 plays (again, holding out {\em Romeo and Juliet} for testing), applying the Moses decoder \cite{Koehn07} to find the best paraphrases. 
Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the system's output towards Shakespeare's style of writing.
We found that performing Minimum Error Rate Training \cite{MERT} using a small set of held out parallel text from Romeo and Juliet was necessary in order to tune the
video corpus baseline to generate reasonable paraphrases.

\subsection{Comparison Using Existing Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of systems targeting Shakespearean English using the previously proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics which
have been demonstrated to correlate with human judgments on semantic adequacy and lexical dissimilarity with the input.
A description of each of the systems compared in this experiment is presented in Table \ref{systems}.  As mentioned in \S \ref{modern_translations}, the Enotes paraphrases diverge little from the original text,
resulting in a BLEU score of 52.3 when compared directly to the original lines from Shakespeare's plays.  Because our goal is to produce paraphrases which make more dramatic stylistic changes to the input,
in the remainder of this paper, we focus on the Sparknotes data for evaluation.

\subsubsection{Discussion}
Two main trends are evident in Figure \ref{bleupinc}.  First, notice that all of the systems trained using parallel text achieve higher BLEU scores than the unmodified modern
translations.  While the dictionary baseline achieves a competitive PINC score, indicating it is making a significant number of changes to the 
input, its BLEU is lower than that of the modern translations.  Secondly, it seems apparent that the systems whose parameters are tuned using Minimum Error Rate Training
tend to be more conservative, making fewer changes to the input and thus achieving lower PINC scores, while not improving BLEU scores on the test data.  Finally
we note that using the larger target language model seems to yield a slight improvement in BLEU score.

@@

\begin{table}[ht]
  \begin{center}
    \begin{tabular}{|l|p{3in}|}
      \hline
      System & Description \\
      \hline
      \hline
      16and7plays\_36LM & Phrase table extracted from all 16 Sparknotes plays (other than R\&J) and language model built from all 36 of Shakespeare's plays, again excluding R\&J.
      Uses default Moses parameters. \\
      \hline
      16and7plays\_36LM\_MERT & Same as 16and7plays\_36LM except parameters are tuned using Minimum Error Rate Training \cite{MERT}. \\
      \hline
      16and7plays\_16LM & Phrase table is built from both Sparknotes and Enotes data, and Language model is built from the 16 plays with modern translations\\
      \hline
      16and7plays\_16LM\_MERT & Same as 16and7plays\_16LM except parameters are tuned using MERT. \\
      \hline
      16plays\_36LM & Only Sparknotes modern translations are used.  All 36 plays are used to train Shakespearean language model.\\
      \hline
      16plays\_36LM\_MERT & Same as 16plays\_36LM except parameters are tuned using MERT. \\
      \hline
      video\_corpus\_baseline & Paraphrase system combining out of domain parallel text \cite{chen11} with an in-domain language model.  Described
      in detail in \S \ref{video_baseline}. \\
      \hline
      modern (no change) & No changes are made to the input, modern translations are left unchanged. \\
      \hline
      Dictionary & Dictionary baseline described in \S \ref{dictionary_baseline}\\
      \hline
    \end{tabular}
  \end{center}
  \caption{Descriptions of various systems for Shakespearean paraphrase.  {\em Romeo and Juliet} is held out for testing.}
  \label{systems}
\end{table}

@@

\section{Human Evaluation}
\label{human_evaluation}
Figure \ref{bleupinc} provides some insight into the performance of the various systems, however it is initially unclear how well the BLEU and PINC
automatic evaluation metrics perform when applied to evaluating paraphrases that target a specific style of writing.  BLEU and PINC have previously
been shown to have high correlation with human judgments of semantic adequacy and lexical dissimilarity of paraphrase candidates, 
but no corresponding work exists for paraphrasing models that target a specific style of writing.

While BLEU is typically used to measure semantic adequacy, it seems reasonable to assume that it 
could also be useful for measuring stylistic alternations, since utterances
are more likely to contain overlapping ngrams if they are both semantically and stylistically similar.  What BLEU cannot tell us, however
is what portion of its improvements are due to stylistic similarity or semantic equivalence.  For this reason, we were motivated perform
an evaluation based on human judgments of semantic adequacy, lexical dissimilarity and stylistic similarity.

For this purpose, we randomly sampled 100 lines from {\em Romeo and Juliet}, then two of the authors annotated each sentence and its Shakespearean
translation to indicate semantic adequacy, lexical dissimilarity, stylistic similarity, and overall quality.
The aggregate results of the human evaluation are displayed in Figure \ref{human_judgements}.  Agreement between annotators
measured using Pearson's $\rho$ is displayed in Table \ref{annotator_agreement}.

Based on the human evaluation, it appears that the baseline combining paraphrases collected from Mechanical Turk \cite{chen11} with
a Shakespearean language model has the highest semantic adequacy, yet this approach is also fairly conservative in that it makes few changes to the input.

The dictionary baseline, and the paraphrase system trained on parallel modern translations are roughly comparable in terms of 
the number of changes made to the input, but the system trained on modern translations achieves higher semantic adequacy, while also being rated higher on style and overall.

These results are roughly in line with the automatic evaluation metrics presented in Figure \ref{bleupinc}.  However we also see several important
trends which are not apparent from the automatic evaluation.
Although the video baseline achieves the highest semantic adequacy in the human evaluation, its BLEU score
is significantly lower than 16plays\_36LM on the Sparknotes data.\footnote{
Note that the BLEU score of 16plays\_36LM is significantly lower when evaluated on the Enotes data.  This makes sense, because the 
16 plays come from Sparknotes. This system is not trained on the 7 Enotes plays which, whose modern translations tend
to be slightly different in style.}
It would appear that in this case BLEU is conflating semantic adequacy with writing style.  Although the paraphrases produced 
by the video baseline have high semantic adequacy, their style tends to differ substantially from the reference translations resulting
in fewer ngram matches, and thus a lower BLEU score.

@@

\section{Automatic Metrics Evaluating Writing Style}
While PINC and BLEU do seem useful for automatically evaluating stylistic paraphrases, BLEU tends to conflate the notions of
semantic adequacy with writing style.  When comparing various systems using automatic metrics, it would seem useful
to separate the effects caused by these two distinct criteria.  We would like our automatic evaluation metrics to be able to distinguish
between a system which generates perfect paraphrases which do not match the target style of writing versus a system which
generates sentences in the correct style, but which convey different meaning.

@@

We present a preliminary evaluation of these metrics by measuring their correlation with human judgments, but
it should be emphasized that we are only evaluating these metrics with respect to one specific style of writing.  We
are optimistic that these results will generalize across writing styles, however, since they are based entirely
on ngram statistics.

@@

\subsection{Evaluation}
We trained both the logistic regression and cosine similarity evaluation metrics using the original Shakespeare plays and modern translations as
the source and target corpus respectively (holding out {\em Romeo and Juliet}), then measured Pearson's Correlation Coefficient between the automatic
evaluation metrics and human judgments described in \S \ref{human_evaluation}.  These results are reported in table \ref{correlation}.

@@

As can be seen in table \ref{correlation}, the correlation between semantic adequacy and BLEU appears smaller than that reported in previous work \cite{chen11}.  Presumably this is
due to the conflation of stylistic differences and semantic adequacy discussed discussed in \S \ref{human_evaluation}.  However it also appears 
that the correlation between BLEU and human style judgments is too low to be of practical use for evaluating style.

@@

\section{Translating Shakespeare's Plays to Modern English}
Finally we perform a preliminary evaluation on the task of automatically translating Shakespeare's plays into modern English.  
%Success at this task could have immediate benefits to students, as well as translators of Shakespeare's plays into modern English.

For the purposes of this evaluation, 
we make use of the same paraphrase systems previously described, but swap the source and target languages.
Additionally, each system makes use of a language model constructed from the 16 modern translations, with {\em Romeo and Juliet} held out for testing.  
510 lines from {\em Romeo and Juliet} were automatically translated into modern English using each system, and the aligned modern 
translations were used as a reference when computing BLEU.  The results of evaluating each of the automatic evaluation metrics on this
data are presented in Figure \ref{shakespeare_to_modern_automatic}.

@@

\begin{figure}
  \includegraphics[width=5in]{figures/shakespeare_to_modern.pdf}
  \caption{Automatic evaluation of paraphrasing Shakespeare's plays into modern English comparing a system based on parallel text (16plays\_16LM), 
  a Dictionary baseline, and a system trained on out of domain parallel monolingual text.  Note that the video corpus baseline achieves low overall
  PINC score, as few phrases in the input match phrases found in its phrase table, resulting in a small number of changes to the input.}
  \label{shakespeare_to_modern_automatic}
\end{figure}

@@

Perhaps most relevant, however, is recent work automatic generation of rhythmic poetry \cite{Greene10}.  This work focuses on automatically generating and translating
poetry in an appropriate meter (e.g. iambic pentameter) using finite-state transducers, but does not investigate the task of paraphrase.  Their generation system
is trained on Shakespeare's sonnets, and they investigate the task of automatically translating Dante's Divine Comedy from Italian to English.
While our work does not address the issue of meter, it should be possible to combine our translation
models with their weighted finite state transducers to produce Shakespearean paraphrase models which produce output in an appropriate meter.

@@

\section{Conclusions}
We have presented the first investigation into the task of automatic paraphrasing while targeting a specific writing style.  We proposed Shakespeare's plays and their
modern translations as a tesbed for this task, and developed a series of paraphrase systems targeting Shakespearean English.  We showed that while existing evaluation
metrics are useful for evaluating paraphrases in this context, BLEU tends to conflate semantic equivalence with writing style giving an incomplete picture of which systems
perform better according to each criteria.

To address this problem, we introduced two new metrics for evaluating writing style, one of which is based on cosine similarity and another based on logistic regression.
We measured correlation between automatic metrics and human judgments, and showed
that our new metrics have better correlation with human judgments than existing metrics in the context of our task.
While this evaluation is limited to one specific style of writing, we are optimistic that these or similar metrics will also perform well when
evaluating paraphrase systems targeting other writing styles.

Finally, we applied these automatic evaluation metrics in an initial investigation into the task of translating Shakespeare's plays into modern English.
%We plan to translate the remaining 20 of Shakespeare's plays, which could be beneficial to students
%of Shakespeare and also to human translators.
